Test author affiliations with lua filters

### 2023-02-06 article.tex
debugged lua issues

%% Fixes long table error with two columns
%% \makeatletter
%% \let\oldlt\longtable
%% \let\endoldlt\endlongtable
%% \def\longtable{\@ifnextchar[\longtable@i \longtable@ii}
%% \def\longtable@i[#1]{\begin{figure}[t]
%% \onecolumn
%% \begin{minipage}{0.5\textwidth}
%% \setlength{\LTcapwidth}{\linewidth}
%% \oldlt[#1]
%% }
%% \def\longtable@ii{\begin{figure}[t]
%% \onecolumn
%% \begin{minipage}{0.5\textwidth}
%% \oldlt
%% }
%% \def\endlongtable{\endoldlt
%% \end{minipage}
%% \twocolumn
%% \end{figure}}
%% \makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={A complete but succinct description of work using relevant important keywords while being snappy when possible},
  pdfauthor={1},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{A complete but succinct description of work using relevant
important keywords while being snappy when possible}
\author{1\textsuperscript{}}
\date{\today}

@@

>>>>

%% Fixes long table error with two columns
%% \makeatletter
%% \let\oldlt\longtable
%% \let\endoldlt\endlongtable
%% \def\longtable{\@ifnextchar[\longtable@i \longtable@ii}
%% \def\longtable@i[#1]{\begin{figure}[t]
%% \onecolumn
%% \begin{minipage}{0.5\textwidth}
%% \setlength{\LTcapwidth}{\linewidth}
%% \oldlt[#1]
%% }
%% \def\longtable@ii{\begin{figure}[t]
%% \onecolumn
%% \begin{minipage}{0.5\textwidth}
%% \oldlt
%% }
%% \def\endlongtable{\endoldlt
%% \end{minipage}
%% \twocolumn
%% \end{figure}}
%% \makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Test author affiliations with lua filters},
  pdfauthor={Jane Doe,1,2,; John Q. Doe,2},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Test author affiliations with lua filters}
\author{Jane Doe\textsuperscript{$\dagger{}$,1,2,*} \and John Q. Doe\textsuperscript{$\dagger{}$,2}}
\date{\today}

@@

\textsuperscript{$\dagger{}$}
These authors contributed equally to this work.

\textsuperscript{1} Acme Corporation\\
\textsuperscript{2} Federation of Planets

\textsuperscript{*} Correspondence:
\href{mailto:jane.doe@example.com}{Jane Doe
\textless{}jane.doe@example.com\textgreater{}}
